### 2010-03-16 papers/icfp-2010-desc/paper_idesc.tex
IDesc@ICFP: introduce tagged index description

@@

>>>>

In Section~\ref{sec:desc-examples}, we have defined a \emph{tagged}
form for descriptions. This format follows the usual presentation of
inductive types as sums of product. With indexed description, this
definition can be generalized. Indeed, when defining an indexed
data-type, we have access to this index. Therefore, we can use this
index to influence the choice of constructors. This captures the
essence of dependent data-types: a term -- the index -- has the
ability to influence the data-type.

For convenience, we divide a tagged indexed description in two parts:
first, the constructors that do not depend on the index; then, the
constructors that do. The non-dependent part mirrors the definition
for non-indexed descriptions: we are provided a finite choice of
constructors. The index-depend part simply indexes the choice of
constructors by $I$. Hence, by inspecting the index, it is possible to
enable or disable the constructors.

\[\stk{
 \ATagIDesc{I} \mapsto \SIGMA{\V{E}}{\EnumU} (\spi{\V{E}}{(\LAM{\_} \IDesc{I})}) \\
 \ITagIDesc{I} \mapsto \SIGMA{\V{F}}{I \To \EnumU} (\PI{\V{i}}{I} \spi{(F\: i)}{(\LAM{\_} \IDesc{I})})  \\
 \TagIDesc{I}  \mapsto \TIMES{\ATagIDesc{I}}{\ITagIDesc{I}}
}\]

In the case of vectors, for instance, for the index $n = \NatZero$, we
would only offer the constructor $\ListNil$. Similarly, for $n =
\NatSuc{n'}$, we only offer the constructor $\ListCons{}{}$. We will
see more instances of this pattern in the following.

@@

\subsubsection{Examples}
